
\begin{rubric}{Miscellaneous Experience}
    \subrubric{Awards and Achievements}
    
    \entry*[2020] \textbf{United Nations (UN) Volunteer:} Selected as an Environmental Researcher on Volunteering basis at Global Waste Cleaning Network (GWCN).

    \entry*[2018] \textbf{Best Project Award:} One Engineering Project entitled 'Extraction and Classification of User Interface Components from an Image' received Best Project Award from Guru Govind Singh Indraprastha University, New Delhi, India.
    %
    \entry*[2018] \textbf{Smart India Hackathon (Annual National Level Coding Competition organised by Govt. of India):} Our Team 'Sakshat' Mentored by me was selected as one of the Finalist Teams out of 2000 entries, in the Smart India Hackathon 2018, Software Edition at a Center at Indore, India
    
    \subrubric{Certification}

    \entry*[2020] \textbf{The International English Language Testing System (IELTS):} Band score of 7.5 overall in IELTS Academic, test conducted by the British Council on 22nd October 2020.

    \entry*[2019] \textbf{Short Term Course of One Week on Digital Signal Processing using MATLAB (DSPM 2019):} Certificate awarded by Netaji Subhas Institute of Technology (A Prominent University under Govt. of Delhi), New Delhi, India.
    
    \entry*[2018] \textbf{Quality Improvement Program of One Week on Machine Learning and its Applications:} Certificate awarded by Indian Institute of Technology (IIT), Roorkee, India.
    
    \entry*[2017] \textbf{Short Term Course of One Week on Information Security and Digital Forensics:} Certificate awarded by Netaji Subhas Institute of Technology (A Prominent University under Govt. of Delhi), New Delhi, India.
    
    \entry*[2017] \textbf{International Workshop on Big Data Analytics (WBDA 2017):} Certificate awarded by Jawaharlal Nehru University (JNU), New Delhi, India.
    
    \entry*[2016] \textbf{Quality Improvement Program of Two Weeks on Parallel Programming for HPC:} Certificate awarded by Indian Institute of Technology (IIT), Delhi, India.
    
    \entry*[2016] \textbf{Workshop on Image Processing using MATLAB:} Certificate awarded by University School of Information and Communication Technology (USICT), New Delhi, India.
    
    \entry*[2016] \textbf{Short Term Course of One Week on Vulnerability Assessment of Networks and Web Applications:} Certificate awarded by National Institute of Technical Teachers Training and Research (Govt. of India), Chandigarh, India.
    
    \entry*[2013] \textbf{Faculty Development Program of One Week on Advanced Communication Techniques:} Certificate awarded by National Institute of Technology (Govt. of India), Delhi, India.
    
    \entry*[2012] \textbf{Quality Improvement Program of Two Weeks on Creativity and Innovation}. Certificate Awarded by Indian Institute of Technology, Delhi, India.
    \end{rubric}